---
title: "Setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(reschola)
```

This vignette describes how to get from a computer with no R or software development tools to a system on which you can do data analysis the Schola way. It is written primarily with Windows systems in mind.

# Overview

[Note on quick option drat]

# Installing R

- R
- packages
- devtools
- R tools
## TBD: renv

# Installing git

## Git GUI

# Optional: LaTex


# Fonts for reschola charts

To be able to produce charts in the default reschola font - Roboto and Roboto Condensed - you need to have these fonts on your machine and registered with R.
The easiest way to do is to run `reschola::import_fonts()` and then install the fonts onto your system from the paths in the messages printed by these functions. 
You can also set the option `reschola.loadfonts` to have `reschola` register these fonts with the PDF/PostScript ecosystem upon package load.





