---
title: "Tips and Tricks for R and Rstudio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tips}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(reschola)
```

This vignette provides some handy tips and tricks for working with R in RStudio. 
For more fundamental principles and guidance on getting R and RStudio setup for the Schola workflow, see the [Setup](setup.html) vignette.
For guidance on the workflow itself, see the [Workflow](workflow.html) vignette.

## RStudio tips

All keyboard shortcuts below are for Windows.
See <https://support.rstudio.com/hc/en-us/articles/200711853-Keyboard-Shortcuts> for all shortcuts on all platforms.


### General helpers

**Code completion*: when typing a function name, press `Tab` and RStudio will show functions/objects which match that name. Use the arrows to navigate the entry you need and press `Tab` again. Likewise with parameters once you are inside parentheses. Note that you can type e.g. `usegitrel` to get a suggestion for `use_github_release()` as RStudio looks intelligently through functions names some_function_name(). (This is also a good reason to use underscores in your own object/function names).

**Paths completion**: when inside quotes, type or press tab and RStudio will suggest files inside the current project.

**Go to anything**: in RStudio, press `ctrl`+ `.`, and start typing. RStudio will suggest files and functions in this project and if you click/arrow+enter into one, will take you to the code.

**Cheatsheets**: in help > Cheatsheets, you can get to two-page cheatsheets on some of the most used packages. They are also [online](https://rstudio.com/resources/cheatsheets/).

**Multiple cursors**: when making changes to similar lines, you can use multiple cursors:  press `alt` and drag up or down or press `ctrl`+`alt`+`up`/`down` to add cursor in the above or below line. Press `ctrl`+`alt` and click to add cursors anywhere. Then type, move around, delete etc.; when done, press `esc`.

**Object view**: holding `ctrl` while clicking on any object name in the code editor lets you view that object: code for functions, dataset viewer for data.

**Accessing help**: pressing `F1` when your curser is on a function name will display the documentatin for that function, same for package names

### Snippets

When you start typing, some of the suggestions are snippets: they are marked 'snippet' and have a paper snippet icon.

If you press tab, they insert bits (e.g. the snippet for `%in%` which appears when you type `in`) of code or mini-templates (e.g. the `fun` snippet). For the mini-templates, you can then `Tab` through the different bits to fill in.

You can also [define your own](https://support.rstudio.com/hc/en-us/articles/204463668-Code-Snippets).

### Handy keyboard shortcuts

- `ctrl`+`enter` runs current line or expression (lines bound by ` %>% `)
- `alt`+`-` inserts `<-`
- `ctrl`+`D` deletes the current line
- `alt`+`M` inserts ` %>% `
- `alt`+`up`/`down` moves the current line/statement up or down
- `ctrl`+`alt`+`up`/`down` copies the current line/statement above or below
- `ctrl`+`shift`+`R` inserts section break in R code (visible in document outline which you can turn on in the top right corner of the code pane)
- `ctrl`+`F10` restarts R (do it often!)

In RMarkdown:

- `ctrl`+`shift`+`enter` runs current chunk in Rmarkdown
- `ctrl`+`alt`+`N` runs next chunk in Rmarkdown
- `ctrl`+`alt`+`P` runs all previous chunk in Rmarkdown
- `ctrl`+`alt`+`I` inserts new chunk in Rmarkdown
- `ctrl`+`click` on a web link to open it in browser

Press `ctrl`+`alt`+`K` in RStudio for an overview of shortcuts.

They can also be customised.

## Retrieving documentation

Besides the F1 key, you can use `?function` to get help for `function` and `??term` to search for `term` in all documentation of all installed packages.

Longer-form documentation for packages is often found in vignettes.
Run `vignette('vignette-name', 'package-name')` to get a particular one.
(Intro vignettes often have the name of the package, e.g. `vignette('reschola', 'reschola')`).
Get list of vignettes for any package `browseVignettes('package-name')`.

## Getting help beyond the documentation

Four resources:

1. Google the error message or its more generic variant if you can figure it out. This may bring you to the other resources.
2. StackExchange: filter for the [`r`](https://stackoverflow.com/questions/tagged/r) tag; likewise, individual packages have their own tags.
3. The [RStudio Community](https://community.rstudio.com/)
4. Twitter [#rstats](https://twitter.com/hashtag/rstats)

When asking for help, provide a minimal [reproducible example](https://reprex.tidyverse.org/articles/articles/magic-reprex.html) if at all possible.

## The `usethis` package: utilities for easy code development

Mostly useful for package development, but some utilities also make your life easier in any project:

- `edit_*` for shortcuts to editing setup files e.g. `.Rprofile`
- `ui_*` for creating nice console output in your code
- `use_git_*` to quickly set up or configure a git repo in your project, link to Github etc.

## Data exploration

- `dplyr::tally(weight = )` / `dplyr::add_tally(weight = )`
- `skimr::skim(df)` / `df %>% group_by(var) %>% skim()`
- [visdat](https://docs.ropensci.org/visdat/) for quick data overview
- [naniar](http://naniar.njtierney.com/) for missing data analysis
- [ggcorrplot](https://cran.r-project.org/package=ggcorrplot) for correlation matrices in `ggplot2`

## Data input

- `data.table::fread()` for faster CSV reading
- [`vroom`](https://vroom.r-lib.org/) for fast CSV reading of large datasets
- `readr::read_csv2()` for reading semicolon-separated CSVs with decimal comma

### From LimeSurvey

- [limer](https://github.com/cloudyr/limer) worked fine when I last used it, but it has been a while.

### From Google sheets / Forms

- see [googlesheets4](https://github.com/tidyverse/googlesheets4)

## Data output

- `readr::write_excel_csv[2]()` for Excel-friendly CSVs

## Data checking

- packages [`validate`](https://cran.r-project.org/web/packages/validate/vignettes/introduction.html), [`assertr`](https://cran.r-project.org/web/packages/assertr/vignettes/assertr.html), [`pointblank`](https://rich-iannone.github.io/pointblank/), [`dlookr`](https://cran.r-project.org/web/packages/dlookr/vignettes/EDA.html)

## Data cleaning

- package [`janitor`](https://cran.r-project.org/web/packages/janitor/vignettes/janitor.html)
- `readr::type_convert()`: 

## Resources for different data types or analysis areas

This section points to packages and resources you can use in different parts of your analysis or to perform various specialised tasks.

### Web scraping

- [rvest](https://rvest.tidyverse.org/) for a scraping tool
- [httr](https://httr.r-lib.org/) for a simple HTTP client

### Modeling

- [broom](https://broom.tidyverse.org/) for extracting model parameters in a consistent way
- [tidymodels](https://github.com/tidymodels/tidymodels.org) for tidy modeling generally

### Spatial data

[sf + guides](https://r-spatial.github.io/sf/articles/sf1.html)

https://geocompr.robinlovelace.net

#### Displaying geospatial data and making maps

- see [Making charts](charts.html) vignette

#### Geodata on Czech Republic

[`CzechData`](https://github.com/JanCaha/CzechData) - recommended:

- provides access to all basic geospatial datasets for CZ (boundaries of admin units, topology of things such as rivers, roads, railways etc.)
- has a set of codebooks and code conversion tables for spatial entities (municipalities etc.)
- provides basic demographic data on municipalities
- not on CRAN but stable and well maintained.

There is also [`RCzechia`](https://cran.r-project.org/package=RCzechia), which is on CRAN.

[`pragr`](https://petrbouchal.github.io/pragr/) provides utilities for mapping Prague.

### Statistical data

- [eurostat](https://cran.r-project.org/package=eurostat): provides intuitive access from R to all Eurostat open data
- [oecd](https://cran.r-project.org/package=OECD): ditto for OECD
- [czso](https://petrbouchal.github.io/czso/): ditto for Czech Statistical Office

### Czech public finance data

[`statnipokladna`](https://petrbouchal.github.io/statnipokladna) provides friction-free access to 

For other related datasets, see Ondřej Kokeš's [`od`](https://github.com/kokes/od) and [`knod`](https://github.com/kokes/knod) (not R, more software-agnostic or Python) and the APIs by [Hlídač státu](https://www.hlidacstatu.cz/) and [CityVizor](https://cityvizor.cz/).

### Time series

- packages `tsibble`, `feasts`, `fable` - see [tidyverts.org](https://tidyverts.org/); [`brolgar`](http://brolgar.njtierney.com/)

### Network data 

[tidygraph](https://tidygraph.data-imaginist.com/)
[ggraph](https://ggraph.data-imaginist.com/) for visualisation

### Text data

[tidytext](Workflow helpers)

## Getting stuff on the web

Two things:

1. Any Rmarkdown document, unless you have tons of LaTex-specific stuff in it, should render into html; just switch the `output` argument in the YAML header to `html_document`.

2. [Netlify](https://www.netlify.com/) is an amazing service that lets you quickly get any website to [something].netlify.com. 

3. For public repositories on Github, you can use the docs/ folder to publish to scholaempirica.github.io/{reponame}, or you can use the gh-pages branch for that. See [Github Pages](https://pages.github.com/).

## Long-form, multipart reports

Have a look at [`bookdown`](https://bookdown.org/)

