---
title: "Getting Started"
output: html_document
---

*This document is just for you, to help you find out how to work with such a project. You can delete it afterwards.*

You have just created a reschola project.

It comes with some files and directories as suggested ways of organising your work:

- `shared.R` for shared variables and perhaps functions. By default contains GDrive URL and project title, if set during setup
- `0_retrieve-data.R` helps you download files from your GDrive folder, if set. You can also use it to store code for retrieving other data. This should only hold things which you expect to only run once, or refresh rarely.
- `00_read-data.R` should hold code that reads the data and does any transformations immediately tied to data reading, e.g. setting data types or basic filtering. Again, this is code that you don't expect to change as you work on the actual analysis. You may want to save the result into `rds` files in `data-intermediate` (or `data-input` if it is simply an `rds` mirror of the input data saved for quick access.)
- `000_check-and-process-data.R` (you may wish to number this one `01_*` to signal that you expect to rerun it often with the rest of the analysis, and you may also turn it into an Rmd file if that is more convenient.) This should process 
- `[NN]_*.Rmd` where NN is 01-98 is the actual analysis - may be an exploratory script, a partial analysis, or a report. Expected to be run in the order of their numbering, but ideally key components should work off data saved in `data-input` or `data-intermediate`.
- `data-input` should contain only unaltered input data as downloaded.
- `data-intermediate` should contain processed data files
- `data-output` should contain data that you expect to share externally that are the output of your project
- `charts-output` and `reports-output` for the obvious
- `99_reproducibility.R` by default contains a description of the system and environment used to run the analysis. Use it to store any other information useful for reproducing the analysis (but not passwords etc.)

You should feel free to move code between the analysis and the `00_*`/`000_*` scripts as you discover data transformations that should be made earlier on in the workflow.

Use `build.R` to tie these together - when run, it should rebuild the whole project from scratch, except perhaps downloading data.
You may want to build different versions of `build_*.R` as helpers for running different parts of the workflow while you work.


You can find guidelines for building Schola Empirica projects by running the following chunk:

```{r setup, include=FALSE}
vignette("workflow", package = "reschola")
```

If you are having trouble setting up your system, see

```{r}
vignette("setup", package = "reschola")
```

For tips on using R and RStudio efficiently, run

```{r}
vignette("tips", package = "reschola")
```

And if you would like to make changes to the rechola package, see

```{r}
vignette("tips", package = "reschola")
```


The whole documentation for the package is online, run the following chunk to go there:

```{r}
browseURL("https://scholaempirica.github.io/reschola")
```
